### 2023-05-15 docs/minutes/slides_19_05/document.tex
test heterodyne run

\begin{frame}[standout]
	Fin.
\end{frame}

@@

\begin{frame}[fragile]{Backup slides}
	Sometimes, it is useful to add slides at the end of your presentation to
	refer to during audience questions.

	The best way to do this is to include the \verb|appendixnumberbeamer|
	package in your preamble and call \verb|\appendix| before your backup slides.

	\themename will automatically turn off slide numbering and progress bars for
	slides in the appendix.
\end{frame}

@@

	\begin{itemize}
		\item Why? Very nasty likelihood curves
	\end{itemize}

	$$  p(\theta | d) \propto p(d | \theta) \pi({\theta})$$
	$$ p(\theta | d) \propto \mathcal{L}(\theta) \pi({\theta})$$

	For uniform prior, posterior shape $\sim$ likelihood shape.

>>>>

\begin{frame}[standout]
	Backup slides
\end{frame}

@@

@@

	\begin{frame}{What changed?}

		AM: What changed such that now everything works?

		\begin{itemize}
			\item Dropping PSR terms to smooth likelihoods
			\item \textit{Increasing} measurement noise  
			\item Don't need too many live points
			\item Non-default Bilby sampler settings 
			\begin{itemize}
				\item e.g. docs recommend `sample=act-walk`or `sample=acceptance-walk`
				\item More success with `sample=rwalk-dynesty` (not `sample=rwalk` which is the Bilby implementation)
			\end{itemize}
		\item Be mindful of float errors - Python/Numpy/Bilby Nans get propagated, rather than error e.g. Fortran.
		\end{itemize}
